Robust receding horizon control for linear systems with state and input dependent disturbances

### 2015-04-22 example.tex
Corrected typo.
Included explicit flop count.

%!TEX root = draft_v2.tex
\section{Complexity}\label{sec:complexity}
The computational complexity of the considered algorithm can easily be bounded. In order to give implementation
free bounds we specify only floating point operations (flops). For each given active set the solver has
to solve at most $2N$ mpQPs, which is done by decomposing the problem as stated in section~\ref{sec:gen:mpQP},
in the worst case this requires one QR decomposition, with $\frac{4}{3}n^3$ flops, and one Cholesky decomposition,
with $\frac{n^3}{3}$ flops, where $n$ is the number of optimisation variables. Solving the worst case problem
on one stage therefore requires $\frac{5}{3}(2n_x^3+n_u^3)$ flops, in the worst case $N$ stages need to be solved,
so that the worst case computational burden for the solution of the mpQP sequence is given 
by~$\frac{5N}{3}(2n_x^3+n_u^3)$. To the authors' best knowledge there are no sensible bounds on the number of
active set changes, so that no bound can be given on the number of times the sequence has to be solved.
In section~\ref{sec:example} we state the case of an example system with an implementation in MATLAB.

@@

The simulation was implemented in MATLAB only using non optimised in-built functions for the main computational
purposes. In the simulation illustrated in figure~\ref{fig:plot} there were a total of 10 iterations required,
out of which 7 correspond to changes of the dominating right hand side of $\mathcal W(x,u)$, for which no recomputation
of the solution is necessary. Performing the entire linesearch to the boundary of the feasible set took $0.3765s$.

>>>>

%!TEX root = draft_v2.tex
\section{Complexity}\label{sec:complexity}
The computational complexity of the considered algorithm can easily be bounded. In order to give implementation
free bounds we specify only floating point operations (flops). For each given active set the solver has
to solve at most $2N$ mpQPs, which is done by decomposing the problem as stated in section~\ref{sec:gen:mpQP}.
For each mpQP the main computational effort is used the computation of $\Sigma$ in~\eqref{seq:sigma}.
In the case~\eqref{eq:sigma:normal}, this requires a QR decomposition with $2(mn^2-n^3/3)$ flops 
($m$ the number of active constraints and $n$ the number of optimisation variables), the inversion of a 
triangular matrix with $(m^3-m)/6$ flops and several matrix multiplications with $mpn$ flops (for the multiplication
of a $m\times n$ matrix with a $n\times p$ matrix).
The computationally more expensive case~\eqref{eq:sigma:degen}, requires a QR decomposition, the inversion of a
definite matrix $W$, which can be done using the Cholesky decomposition with $n^3/3$ flops and the inversion of a 
triangular matrix, it again requires several matrix multiplications and additions with $mn$ flops and one additional 
inversion of a definite matrix $\Delta$. In the worst case this adds up to $11n^3+n^2-n/3$ flops to obtain $\Sigma$
in the worst case scenario. The solution to the problem is then the result of a matrix multiplication, in order to 
be able to solve the subsequent mpQP the matrix $W_\theta$ and the vector $c_\theta$ have to be computed so that the over
all flop count in the worst case adds up to $11n^3+n^2+2/3n+2n^2 n_\theta$, where $n_\theta$ denotes the dimension of the
parameter~$\theta$. At each stage two mpQPs have to be solved recursively, so that in the worst case the recursion
for the entire horizon requires $N(2 n_x+5 n_x^2+101 n_x^3+8 n_x^2 (n_u+n_x))$ flops.

To the authors' best knowledge there are no sensible bounds on the number of
active set changes, so that no bound can be given on the number of times the sequence has to be solved.
In section~\ref{sec:example} we state the case of an example system with an implementation in MATLAB.

@@

The simulation was implemented in MATLAB only using non optimised built-in functions for the main computational
purposes. In the simulation illustrated in figure~\ref{fig:plot} there were a total of 10 iterations required,
out of which 7 correspond to changes of the dominating right hand side of $\mathcal W(x,u)$, for which no recomputation
of the solution is necessary. Performing the entire linesearch to the boundary of the feasible set took $0.3765s$.
